\plaintitle

### 2016-09-12 drafts/labor/complexity.tex
closing the book on decomposition

@@

@@

  \endnotetext{
  \section{Complexity notes}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work%
,     exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing''%
,     the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

    This is also kind of off-topic, isn't it? where to take it?

    \topic{A smaller but growing body of work has reflected on this
    and brought to our attention a number of ethical questions surrounding the
    increasing complexity of crowdwork and the hazards that increasingly arise.}
    \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
    --- working for increasing amounts of time on tasks of growing complexity%
,     only to discover that requesters are not willing to pay%
,     for instance ---
    but these and other dangers range an enormous landscape
    \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

    \topic{We summarize the work discussed so far in this way:
    researchers of crowdsourcing and on--demand labor in general
    have attempted to find the characteristics which
    enable and stymie successful applications of this form of work%
,     and how to get past or around these boundaries.}
    Whether this work has focused on the self (as in the case of ``selfsourcing'')
    or on others (as in \textit{CrowdForge} and \textit{Foundry})%
,     crowdsourcing literature has generally studied the constituent work
    and attempted either to work around
    or indeed with
    the limitations of crowdwork to accomplish a difficult task
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

    Crowdforge, turkomatic, others talk about limiting factors; bring them up

      Talked to someone about this section and got some feedback\dots
      \begin{enumerate}
        \item Explain what ``clever arrangement of work'' in the first paragraph means
              (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
        \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
              (maybe even to justify its placement here); and
        \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
              to make the historical stuff on piecework
              directly speak to the three previous paragraphs.
        \item (Maybe?) summarize the piecework stuff
              (the last paragraph approaches that, but more could be done).
      \end{enumerate}
      Thoughts on this?

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber%
,   where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited%
,   we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
}

>>>>

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowdwork already.}
As \citeauthor{hart2013rise} described,
the 1930s saw a flourishing of clever piecework job design out of necessity
due to the fact that it was infeasible to provide new workers with
the comprehensive education that was familiar to men
\cite{hart2013rise}.
This constraint led to much more tightly scoped work, and
(perhaps surprisingly at the time) more efficient allocations of workers,
who could now specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.

@@

Finally, and perhaps most importantly,
we need to replicate the success of narrowly slicing education and training for expert work
as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
\cite{hart2013rise,grier2013computers}.
That is, we need to identify new ways to train crowdworkers for uniquely narrowly defined work.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowdworkers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower crowdworkers to do complex work such as engineering and metalworking,
rather than doom them to match girl reputations:
``brash, irregular, immoral, and uneducated''
\cite{10.2307/3827491}.

@@

%   \endnotetext{
% %     \topic{We summarize the work discussed so far in this way:
% %     researchers of crowdsourcing and on--demand labor in general
% %     have attempted to find the characteristics which
% %     enable and stymie successful applications of this form of work%
% % ,     and how to get past or around these boundaries.}
% %     Whether this work has focused on the self (as in the case of ``selfsourcing'')
% %     or on others (as in \textit{CrowdForge} and \textit{Foundry})%
% % ,     crowdsourcing literature has generally studied the constituent work
% %     and attempted either to work around
% %     or indeed with
% %     the limitations of crowdwork to accomplish a difficult task
% %     \cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

% %     Crowdforge, turkomatic, others talk about limiting factors; bring them up

%       % Talked to someone about this section and got some feedback\dots
%       % \begin{enumerate}
%       %   \item Explain what ``clever arrangement of work'' in the first paragraph means
%       %         (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
%       %   \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
%       %         (maybe even to justify its placement here); and
%       %   \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
%       %         to make the historical stuff on piecework
%       %         directly speak to the three previous paragraphs.
%       %   \item (Maybe?) summarize the piecework stuff
%       %         (the last paragraph approaches that, but more could be done).
%       % \end{enumerate}
%       % Thoughts on this?

% %   \citeauthor{10.2307/23702539} also argues that
% %   a significant obstacle to the introduction of piecework in railroad shops was
% %   the resistance of workers
% %   (the other being the resistance of management (for different and varying reasons)).
% %   In the cases of online platforms like AMT and digitally mediated platforms like Uber%
% % ,   where in both cases workers rarely
% %   if ever
% %   interact face--to--face and
% %   opportunities for coordination and collective action are severely limited%
% % ,   we should expect to see
% %   the challenges stymieing collective action
% %   that we see in \citeauthor{dynamo} and elsewhere
% %   \cite{10.2307/23702539,dynamo}.
% }

### 2016-09-12 drafts/labor/decomposition.tex
complexity should be kind of done
closing the book on decomposition

\subsubsubsection{\crowdworkpers}
% \ali{Does this belong here at all? The complexity argument just dives in.}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks%
, and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work)%
, the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes%
, the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT%
, and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996%
,       Cai:2015:WLW:2702123.2702267}.
Yet more work looks at the general framing of tasks%
, chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks%
, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
, we as a community have leaned \textit{into} the peril of
low--context work%
, ``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

Not all of the work toward optimizing crowd work--flows has gone toward
minimizing the creative input of crowd workers;
a thriving body of literature adopts
practices such as pipelining to allow experts to participate in crowd work
\cite{foundry}.

@@

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
\ali{I could point out that the opportunity to check work and
repeat the task is a little like find--fix--verify, but is that jumping the gun?}
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

@@

\ali{\citeauthor{marx2012economic} in here? Alienated from the context of the work?
Critiques about piecework marginalizing workers?
\citeauthor{american1921problem} wrote about this as well
(albeit they were advocating from workers' perspectives, but who isn't?)}

\subsubsubsection{\whatchanged}
\begin{inlinelist}
  \item Computers make it possible to switch from one task to another
  unlike any arbitrary manufacturing factory possibly could;
  \item we've sliced works to such small sizes that the marginal costs
  --- things like task--finding, cognitive load switching, etc\dots ---
  have become relatively large;
  \item instrumentation has become so advanced that
  the curve of diminishing value on measuring and tracking workers has shifted significantly
  (but not been obliterated);
  \ali{some companies have suggested self--tracking through
  programs that give workers fitbits and whatnot --- I could make the argument that
  this is just an illustration of that, but
  it's not really about work \textit{per se} unless
  you think about it as the general management of workers. Thoughts?}
\end{inlinelist}

@@

  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Slicing notes}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be%
,     and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do%
,     but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management%
,             and how piecework literature tried to measure everything%
,             but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}

    As a result, the prevalent mindset of designing work for crowd workers
    --- one which treats micro task workers as
    ``modular, protocol--defined computational services'' ---
    has inexorably alienated workers from the greater context of their work
    \cite{irani2015cultural}.

    \ali{i don't like this section \textit{here}, but i like it in general. what do?}
    \topic{One of the emergent properties of micro--tasks has been the relative cost of
    \textit{finding} worthwhile tasks.}
    The research community has documented and to some extent attempted to intervene in
    the discovery of worthwhile tasks
    \cite{taskSearch}.
    \citeauthor{Cosley:2007:SUI:1216295.1216309}
    attempts to address this by
    directing workers to tasks through
    ``intelligent task routing''
    \cite{Cosley:2007:SUI:1216295.1216309}.
    Much of this work and the work at the periphery of this space, then%
,     has focused on
    minimizing the amount of time that people need to spend doing
    anything other than the work for which they are paid.

    What we take away from this and the previous set of work is that
    the value of adopting crowdsourcing for any particular task
    seems to be mediated by two questions:
    \begin{inlinelist}
      \item How long does it take to train workers to do the work in question? and
      \item How long does it take for the worker to do the work?
    \end{inlinelist}
    Minimizing these criteria has become
    the overarching motivation of the crowdsourcing work design community
    \cite{cheng2015break,Newell:2016:OMA:2858036.2858490}

  }

>>>>

\subsubsubsection{\crowdworkpers}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks%
, and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work)%
, the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes%
, the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT%
, and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996%
,       Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
\citeauthor{Cosley:2007:SUI:1216295.1216309}
attempts to address this by
directing workers to tasks through
``intelligent task routing''
\cite{Cosley:2007:SUI:1216295.1216309}.
Much of this work and the work at the periphery of this space, then%
, has focused on
minimizing the amount of time that people need to spend doing
anything other than the work for which they are paid.

Yet more work looks at the general framing of tasks%
, chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks%
, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
, we as a community have leaned \textit{into} the peril of
low--context work%
, ``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

@@

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

@@

\subsubsubsection{\whatchanged}
 \topic{A number of factors in crowdwork are different from piecework,
 chief among them being the relative ease with which
 the metaphorical ``assembly line'' can be changed.}
 Computers make it possible to switch from one task to another
unlike any arbitrary manufacturing factory possibly could;
a worker could do any number of
different \textit{types} of tasks in the span of just a few minutes
\cite{delayAndOrderLasecki}.
This has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to measure consistently as few as 20 years ago
\cite{cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

Further, we've sliced work to such small scales that the marginal activities
--- things like finding work, cognitive task switching, etc\dots ---
have become relatively large compared to the tasks themselves
\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools, mining equipment, or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own
\cite{hart2013rise}.

Rather than fall into the trap that \citeauthor{irani2015cultural} warns of,
--- one which where crowdworkers are rendered as
``modular, protocol--defined computational services'' ---
we may yield better results from crowdwork if we think of workers as similar to
specialized, repurposable tools
\cite{irani2015cultural}.
\ali{feeling meh about this argument\dots}

Finally, instrumentation has reached a sufficiently advanced and ubiquitous point that
the dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable, but trivial
\cite{waltz2012quantified}.
One of the major challenges \citeauthor{10.2307/23702539} cites as
preventing scientific management from being fully utilized,
the difficulty of tracking work \& workers, no longer exists
\cite{10.2307/23702539}.

\subsubsubsection{\implication}
Crowdwork research today is on the right track to investigate pipelining and meta--task design.
That is, investigating better work discovery methods, producing tools for workers to make more informed decisions
\cite[see, for example,][]{turkopticon}.
It's not clear how much benefit there is in the further decomposition of work,
given that we've hit bottlenecks with the cognitive stresses of switching between tasks
as \citeauthor{delayAndOrderLasecki} highlight
\cite{delayAndOrderLasecki}.

@@

  % \clearpage
  % \nobalance{}
  }
%   \endnotetext{
% %     \section{Slicing notes}
% %     The finding here is that
% %     crowdwork can be more carefully micro--managed than piecework could be%
% % ,     and that this is a double--edged sword:
% %     we can effectively give feedback to workers on everything they do%
% % ,     but this is emboldening us to try to
% %     over--manage workers just as piecework tried to do.

% %     My goal for this section is to make two points:
% %     \begin{enumerate}
% %       \item show how this is related to the assembly line and scientific management%
% % ,             and how piecework literature tried to measure everything%
% % ,             but found it untenable given the extra equipment that was necessary
% %             (but generally which didn't exist)
% %             to track every movement and action that workers took.
% %       \item show how this work was enabled by the ``verifiability'' of work output(?)
% %     \end{enumerate}

%     % \ali{i don't like this section \textit{here}, but i like it in general. what do?}

%   }

### 2016-09-12 drafts/labor/relationships.tex
closing the book on decomposition

\subsubsection[the relationships of workers]{???}
\label{sec:relationships}

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition,
    variability of worker performance,
    and uncertainty about good versus bad--faith actors as open questions of crowdwork
    \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

    Earlier we discussed \citeauthor{cheng2015break}'s work
    measuring the impact that interruption has on worker performance
    \cite{cheng2015break}.
    This work illustrates a broader sentiment in
    both the study and practice
    of crowdwork, that microtasks should be designed resiliently against the variability of workers,
    fully exploiting the abstracted nature of each piece of work
    \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
    That is to say, micro--tasks should be designed such that a single worker's poor performance,
    or a good worker's sudden departure,
    does not significantly impact the agenda of the work as a whole.
    While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
    in the form of higher cumulative time to complete
    (albeit much shorter real time to complete, owing to parallelization),
    \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
    similar tasks together
    \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

    \citeauthor{embracingErrorKrishna} take a different approach;
    by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
    the authors offer orders--of--magnitude improvements
    in various binary classification tasks
    \cite{embracingErrorKrishna}.
    And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
    some researchers have designed work predicated on the expectation of it instead:
    \citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
    crowd workers would never be given enough information to piece together sensitive information about
    any single topic
    \cite{sensitiveTasks}.

    The work thus far seems to attempt to maximize the quality of work among workers through various means:
    \begin{inlinelist}
      \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju},
      \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
      \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
    \end{inlinelist}.

@@

    In the field of piecework,
    the research covering this topic has both explored
    a breadth of tasks that might be rendered doable by piecemeal workers
    \textit{as well as} longitudinally documented the success of these approaches.
    Here, we \ali{\dots?}
}
\theendnotes
\end{document}

>>>>

\subsubsection[the relationships of workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}
\subsubsubsection{\crowdworkpers}
\topic{A number of ethical questions surrounding the
    increasing complexity of crowdwork and the hazards have increasingly arisen.}
    \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
    --- working for increasing amounts of time on tasks of growing complexity%
,     only to discover that requesters are not willing to pay%
,     for instance ---
    but these and other dangers range an enormous landscape
    \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
  % \clearpage
  % \nobalance{}
  }
  \endnotetext{
    \section{Flexibility notes}
    A number of researchers have identified
    worker attrition%
,     variability of worker performance%
,     and uncertainty about good versus bad--faith actors as open questions of crowdwork
    \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
    \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
    \& workers who are merely responding in kind to bad requesters
    --- and the broader questions surrounding
    the roles that requesters as well as workers should play ---
    but let it suffice to say that
    requesters have been trying to understand and manage what appears to them as inconsistent work.
    Their ways of responding to that variance in work quality has largely involved
    making the work more flexible and resilient to work
    (although some work has gone into investigating the causes, rather than treating the symptoms)}

    Earlier we discussed \citeauthor{cheng2015break}'s work
    measuring the impact that interruption has on worker performance
    \cite{cheng2015break}.
    This work illustrates a broader sentiment in
    both the study and practice
    of crowdwork, that microtasks should be designed resiliently against the variability of workers%
,     fully exploiting the abstracted nature of each piece of work
    \cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
    That is to say, micro--tasks should be designed such that a single worker's poor performance%
,     or a good worker's sudden departure%
,     does not significantly impact the agenda of the work as a whole.
    While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
    in the form of higher cumulative time to complete
    (albeit much shorter real time to complete, owing to parallelization)%
,     \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
    similar tasks together
    \cite[respectively]{cheng2015break,delayAndOrderLasecki}.

    \citeauthor{embracingErrorKrishna} take a different approach;
    by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds%
,     the authors offer orders--of--magnitude improvements
    in various binary classification tasks
    \cite{embracingErrorKrishna}.
    And rather than building tasks to \textit{tolerate} worker drop--off and attrition%
,     some researchers have designed work predicated on the expectation of it instead:
    \citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
    crowd workers would never be given enough information to piece together sensitive information about
    any single topic
    \cite{sensitiveTasks}.

    The work thus far seems to attempt to maximize the quality of work among workers through various means:
    \begin{inlinelist}
      \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju}%
,       \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
      \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
    \end{inlinelist}.

@@

    In the field of piecework%
,     the research covering this topic has both explored
    a breadth of tasks that might be rendered doable by piecemeal workers
    \textit{as well as} longitudinally documented the success of these approaches.
    Here, we \ali{\dots?}
}
% \theendnotes
\end{document}
